Synthesizing Symmetric Lenses

### 2019-01-27 papers/SymmetricLenses/main.tex
minor fixes

Synthesizing simple symmetric lenses is substantially more challenging that
synthesizing bijective lenses: Since some of the information on each side can be
``disconnected'' from the other side, there will in general be {\em many} lenses
that agree with a given example. To guide the search process, we use {\em
  stochastic regular expressions} and ideas from information theory to estimate
the amount of information propagated by a candidate lens, in conjunction with
annotations to state whether certain bits of information are irrelevant, or must
be maintained.

@@

We added this synthesis procedure to the Boomerang implementation and evaluated
its effectiveness on a benchmark suite of 48 problems, including data-cleaning
tasks taken from Flash Fill~\cite{gulwani-popl-2014}, view-maintenance tasks
taken from Augeas~\cite{augeas2}, and ad-hoc synchronization tasks from a
variety of other sources (mostly from the bidirectional programming literature).
The ``programmer'' can control the search process via examples and annotations
that informs the synthesis algorithm as to whether certain information is
irrelevant, or must maintained.

>>>>

Synthesizing simple symmetric lenses is substantially more challenging than
synthesizing bijective lenses: Since some of the information on each side can be
``disconnected'' from the other side, there will in general be {\em many} lenses
that agree with a given example. To guide the search process, we use {\em
  stochastic regular expressions} and ideas from information theory to estimate
the amount of information propagated by a candidate lens, in conjunction with
annotations to state whether certain bits of information are irrelevant to the
lens, or must be maintained.

@@

We added this synthesis procedure to the Boomerang implementation and evaluated
its effectiveness on a benchmark suite of 48 problems, including data-cleaning
tasks taken from Flash Fill~\cite{gulwani-popl-2014}, view-maintenance tasks
taken from Augeas~\cite{augeas2}, and ad-hoc synchronization tasks from a
variety of other sources (mostly from the bidirectional programming literature).
The ``programmer'' can control the search process via examples and annotations
that informs the synthesis algorithm as to whether certain bits of information
are irrelevant, or must maintained.
